Airspace configuration decision based on Monte-Carlo tree search

### 2018-02-01 article/article.tex
(+) soft constraints

>>>>

Other soft constraints appear to be relevant to have a better modelisation of
the problem. For instance in~\cite{sergeeva2017dynamic} and~\cite{bedouet2016} a
coordination cost is defined. It represent the surplus of work added by the
number of flights travelling from a sector to an other. The shape of the
resulting sector is considered, as the simpler is
the shape, the easier it is to manage, therefore complex shapes are avoided,
by introducing compactness in~\cite{jagare2013constraint} and balconies
in~\cite{sergeeva2017dynamic}. To smooth the transition between two
configurations, the work associated with the realocation of one or more modules
is evaluated. This can be used in a cost function aimed to be minimized
(in~\cite{bedouet2016}).
